---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 1"
author: "Cat Seitz"
date: "Jan. 24, 2023"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(dsbox) 
```

```{r load-data, message = FALSE}
states <- read_csv("data/states.csv")

```

### Exercise 1

```{r dennys dataset dimensions}

nrow(dennys)
ncol(dennys)

```

There are 1643 rows and 6 columns. Each row is a Dennys address, and the variables include the address, city, state, zip code, longitude, and latitude.  

### Exercise 2

```{r quinta dataset dimensions}

nrow(laquinta)
ncol(laquinta)

```

There are 909 rows and 6 columns. This dataset has the same variables as the Dennys dataset, but each row is a La Quinta address. 

### Exercise 3

La Quinta are located in Canada, Mexico, China, New Zealand, Turkey, United Arab Emirates, Chile, and Colombia. Dennys are only located in the US, in every state except Delaware. 

### Exercise 4

Since country is not a variable, we could potentially use the state or zip code variables to distinguish between within or outside the US. If the dataset used specific state codes for outside countries or if zip codes for other countries follow a different pattern than the US, then we can use this information to create a new column titled something like "in_usa" and have responses be "yes" or "no." Or, we can do what is suggested in the lab (which seems easier) and filter items that have a state not in the state dataframe. 

### Exercise 5

```{r any dennys outside usa}

dennys %>%
  filter(!(state %in% states$abbreviation))

```

There are no Denny's location outside the U.S., which confirms what we found on the website in exercise 3. 

### Exercise 6

```{r add country column to Dennys dataset}

dennys %>%
  mutate(country = "United States")

```

### Exercise 7

```{r La Quinta outside US locations}

laquinta %>%
  filter(!(state %in% states$abbreviation))

```

Create a tibble of the location of La Quintas outside the US. Looks like there are only 14 locations. 

### Exercise 8

``` {r add country column to La Quinta dataset}

laquinta %>%
  mutate(country = case_when(
    state %in% states$abbreviation     ~ "United States",
    state %in% c("ON", "BC") ~ "Canada",
    state == "ANT"           ~ "Colombia",
    state %in% c("QR", "AG", "CH", "NL", "VE", "PU", "SL") ~ "Mexico",
    state ==  "FM" ~ "Honduras"
  ))

```

Got the code to work, but the locations we have in this dataset do not line up with what La Quinta has on their website. This could be because the dataset has not been updated since new locations were introduced. 

